Step 12: Export Results

### 2025-09-08 reanalysis-12-export_results.qmd
export

>>>>

## Forest Plot (Publication Style)

```{r forest-plot}
#| fig.width: 10
#| fig.height: 8

# Prepare data for forest plot
forest_data <- results_df[!is.na(results_df$or), ]  # Remove any failed methods

# Add method labels (clean up underscores and format nicely)
forest_data$method_label <- gsub("_", " ", forest_data$method)
forest_data$method_label <- gsub("nearest ", "Nearest Neighbor ", forest_data$method_label)
forest_data$method_label <- gsub("subclass glm", "Subclassification GLM", forest_data$method_label)
forest_data$method_label <- gsub("cbps", "CBPS", forest_data$method_label)
forest_data$method_label <- gsub("entropy", "Entropy Balancing", forest_data$method_label)
forest_data$method_label <- gsub("bart", "BART", forest_data$method_label)
forest_data$method_label <- gsub("twang gbm", "IPTW Twang GBM", forest_data$method_label)
forest_data$method_label <- gsub("glm", "GLM", forest_data$method_label)
forest_data$method_label <- gsub("gam", "GAM", forest_data$method_label)
forest_data$method_label <- gsub("gbm", "GBM", forest_data$method_label)
forest_data$method_label <- gsub("lasso", "LASSO", forest_data$method_label)
forest_data$method_label <- gsub("rpart", "RPART", forest_data$method_label)
forest_data$method_label <- gsub("mahalanobis", "Mahalanobis", forest_data$method_label)

# Add colors (blue for twang_gbm, black for others)
forest_data$color <- ifelse(forest_data$method == "twang_gbm", "blue", "black")

# Create the plot matching results-summary.Rmd style exactly
forest_plot <- ggplot(forest_data, aes(x = reorder(method_label, or), y = or, color = color)) +
  geom_pointrange(aes(ymin = or_ci_lower, ymax = or_ci_upper), size = 0.8) +
  geom_point(size = 3) +
  geom_text(aes(label = sprintf("%.2f", or), color = color), 
            vjust = -1.2, hjust = 0.5, size = 4) +
  coord_flip() +
  scale_color_identity() +
  scale_y_continuous(breaks = seq(1, max(forest_data$or_ci_upper), by = 0.1)) +
  scale_x_discrete(expand = c(0.075, 0.075)) +
  theme_minimal(base_size = 14) +
  labs(
    x = element_blank(),
    y = "Odds Ratio",
    title = "Doubly Robust Propensity Score Adjusted\n Model Estimates (ATT)",
    caption = "\n\nOdds Ratio of 1.0 = No Association.
               MatchIt, WeightIt, and twang R packages are used for estimation.
               IPTW = Inverse probability of treatment weighting.
               IPTW Twang GBM results (shown in blue) reported throughout paper."
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", margin = ggplot2::margin(b = 15)),
    legend.position = "none",
    axis.line = element_line(color = "gray80"),
    axis.text = element_text(color = "gray30"),
    axis.ticks = element_line(color = "gray80"),
    axis.title.x = element_text(margin = ggplot2::margin(t = 10)),
    plot.caption = element_text(margin = ggplot2::margin(t = 15)),
    plot.margin = ggplot2::margin(20, 20, 30, 20)
  ) +
  geom_hline(yintercept = 1, linetype = "solid", color = "gray60") +
  annotate("text", x = 0.5, y = 1, label = "Null", vjust = -1, hjust = 1.2, 
           color = "gray50", size = 3.5)

# Display the plot
print(forest_plot)

# Save the plot
forest_plot_file <- file.path(export_dir, "forest_plot_publication.png")
ggsave(
  filename = forest_plot_file,
  plot = forest_plot,
  width = 10,
  height = 8,
  dpi = 300
)

log_message(paste0("Forest plot saved to: ", forest_plot_file))
cat("\nForest plot (publication style) saved to:", forest_plot_file, "\n")
```
